---
title: "maths"
author: "nikoya"
date: "2023-02-04"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
```{r}
library(knitr)
library(tidyverse)

```
##Q1

a)Continuous
b)Continuous
c)discrete
d)categorical/Ordinal
e)categorical/Ordinal
f)Categorical/ordinal
g)Discrete
h)Categorical/Ordinal
i)Continuous
j)Categorical/ordinal
k)Categorical/ordinal
l)Continuous


```{r}
Position<-c("Labourer","Receptionist","Management Asst 1","Management Asst 2","Junior executive 1","Junior executive 2","Accountant","CEO")
experience<-c(1,1,1,2,2,3,2,3)
salary <-c(10000,15000,25000,30000,40000,50000,100000,800000)

employee<-data.frame(Position,salary,experience)
employee
view(employee) #TO VIEW THE DATA SET

```
##Q2a)
```{r}

salary <-c(10000,15000,25000,30000,40000,50000,100000,800000)
mean(employee$salary)
```
##Q2b)
The median is better,This data set contains a large range of salaries,And salary 800000 has a large effect on the mean and it has outliers as well

##Q2c)
```{r}
weighted.mean(employee$salary, employee$experience)

```

##Q3a)
```{r}
summary(employee$salary)
```
##Q3b)

```{r}
library(graphics)
salary <-c(10000,15000,25000,30000,40000,50000,100000,800000)
boxplot(salary/1000, horizontal =TRUE, xlab ="Salary(inthousands)")

```
##Q3c)

```{r}
data <- c(10000, 15000, 25000, 30000, 40000, 50000, 100000, 800000)

# variance
variance <- var(data)

# standard deviation
sd <- sqrt(variance)

# interquartile range (IQR)
iqr <- IQR(data)

# median absolute deviation (MAD)
median <- median(data)
median_abs_deviation <- median(abs(data - median))

# print results
cat("Variance:", variance, "\n")
cat("Standard Deviation:", sd, "\n")
cat("Interquartile Range:", iqr, "\n")
cat("Median Absolute Deviation from the Median:", median_abs_deviation)

```

##Q4
```{r}
set.seed(123) # set seed for reproducibility
sample_data <- rnorm(100, mean = 50, sd = 10)
hist(sample_data, breaks = 10, main = "Histogram of Normal Distribution (mean = 50, sd = 10)", xlab = "Values", ylab = "Frequency", col = "blue")



```
```{r}
set.seed(123) # set seed for reproducibility
sample_data <- rnorm(100, mean = 50, sd = 10)

# Plotting the histogram
hist(sample_data, breaks = "FD", main = "Density Plot of Normal Distribution (mean = 50, sd = 10)", xlab = "Values", ylab = "Density", col = "blue", border = "white", freq = FALSE)

# Adding the density plot
lines(density(sample_data), col = "red")


```
```{r}
set.seed(123) # set seed for reproducibility
sample_data <- rnorm(100, mean = 50, sd = 10)

# Calculating the percentiles
p25 <- quantile(sample_data, probs = 0.25)
p40 <- quantile(sample_data, probs = 0.40)
p60 <- quantile(sample_data, probs = 0.60)
p75 <- quantile(sample_data, probs = 0.75)

# Displaying the percentiles
cat("25th percentile:", p25, "\n")
cat("40th percentile:", p40, "\n")
cat("60th percentile:", p60, "\n")
cat("75th percentile:", p75, "\n")

```

```


```

